A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-09-09 paper/ms.tex
update ms

Comparing our young star list against the Kepler field yielded two
discoveries.  The first, to be discussed in an upcoming analysis by
J.~Curtis et al{.}, is that Kepler observed the $\approx$350\,Myr open
cluster Theia\,520 (UBC\,1).  At least six Kepler planets are known in
the cluster from the Kepler-52 and Kepler-968 systems
\citep{rowe_validation_2014,jontof-hutter_following_2021}.  The second
discovery, and the focus of this work, is that Kepler observed a
portion of the $\delta$\,Lyr cluster (Stephenson-1; Theia~73;
\citealt{stephenson_possible_1959}).  Figure~\ref{fig:skychart} shows
the overlap between the Kepler field and the cluster.

A previous clustering analysis of the Gaia data reported that
Kepler\,1627 (KIC 6184894; KOI 5245; TIC 120105470) is a member of the
\cn\ \citep{kounkel_untangling_2019}.  Given the previous statistical
validation the close-in mini-Neptune Kepler 1627b
\citep{2012ApJS..199...24T,morton_false_2016,thompson_planetary_2018},
we examined the age of the star and its putative host cluster more
closely (Section~\ref{sec:cluster}).  We find that the $\delta$ Lyr
cluster is \clusterage\ old, and that \sn\ is indeed a member of the
cluster.  Focusing on the planet itself, we confirm that despite the
presence of a previously unreported binary companion, the planet
orbits the G-dwarf primary on an orbit that appears aligned with the
stellar rotation axis (Section~\ref{sec:planet}).  We conclude by
highlighting broader implications for our ability to age-date a
statistical sample of planets (Section~\ref{sec:conc}).

@@

The final piece of evidence \pn\ comes from a spectroscopic
transit we measured from Keck/HIRES during the night of 7 Aug 2021
(UT), using the iodine cell for the wavelength calibration.  We
scheduled the transit using the ephemeris of
\citet{holczer_transit_2016}, which we verified using the available
TESS data.  We also acquired simultaneous multi-band photometry using
MuSCAT3 to help interpret the radial velocities \citep{Narita_2020}.
The lower panels in Figure~\ref{fig:obliquity} show the results.  The
photometry shows the expected starspot trend, along with the transit
and a likely starspot crossing event at ${\rm JD} - 2459433 = 0.955$.
The radial velocities show significant scatter, and a significant
increase in RV is seen shortly after the expected ingress.  The
internal uncertainties on the RVs ($\approx 15\,{\rm m\,s}^{-1}$) is
dominated by the $v\sin i$ broadening.

@@

We fitted the RVs using the \citet{hirano_analytic_2010,hirano_2011}
models for the Rossiter-McLaughlin (RM) effect, and allowed the
sky-projected obliquity, the stellar equatorial velocity, and the
Gaussian dispersion of the spectral lines to vary.  We also allowed
for an optional linear and quadratic trend, and a white-noise jitter
term.  The quadratic model with the RM effect is shown in
Figure~\ref{fig:obliquity}; the prior on $v\sin i$ has been
assumed from Table~\ref{tab:starparams}.  We found $\chi^2_{\rm red} =
5.4$ for the best-fitting linear case, and $\chi^2_{\rm red} = 4.4$
for the best-fitting quadratic, with a $\Delta {\rm BIC} = {\rm
BIC}_{\rm line} - {\rm BIC}_{\rm quad} = 19.6$ and $\Delta {\rm AIC} =
{\rm AIC}_{\rm line} - {\rm AIC}_{\rm quad} = 20.6$.  While this
provides strong statistical evidence to prefer the quadratic model
over the linear one, the $\chi^2_{\rm red}$ indicate that neither fit
is very good.  Considering a quadratic trend alone without any RM
effect yields $\chi^2_{\rm red} = 4.3$, and $\Delta {\rm BIC} = {\rm
BIC}_{\rm trend} - {\rm BIC}_{\rm quad} = 1.9$ ($\Delta {\rm
AIC}=5.2$).  From a model-comparison standpoint, there is therefore
only weak statistical evidence to prefer the best-fitting ``RM and
quadratic trend'' model over the best-fitting ``quadratic trend only''
model.  Given the expected semi-amplitude of the velocity anomaly
($\Delta v_{\rm RM}\approx 20\,{\rm m\,s}^{-1}$) and the actual
achieved precision, the claim of having detected the Doppler transit
is marginal at best.  From the MuSCAT3 data however, we do know that
the transit was observed, and the increase in radial velocity seen
shortly after ingress is more consistent with a prograde or polar
orbit than a retrograde orbit.  Fixing the orbit to be either exactly
prograde or exactly retrograde, we find $\Delta {\rm BIC} = {\rm
BIC}_{\rm retrograde} - {\rm BIC}_{\rm trend} = 18.0$; the retrograde
case is ruled out on this basis.  More precise data will be needed
however to make a more precise obliquity measurement.

@@

Kepler\,1627Ab provides a new extremum in the ages of the Kepler
planets, and opens multiple avenues for further study.  More precise
observations of the Doppler transit could yield a more precise stellar
obliquity, and a means for verifying the expected prograde orbit.
Similarly, transit spectroscopy aimed at detecting either hydrogen or
helium absorption could yield insight into the stability of the
planet's atmosphere \citep[{\it
e.g.},][]{spake_helium_2018,vissapragada_2020}.  A more challenging
measurement would be to determine the planet's mass, either through
detailed timing analyses of the Kepler data, or through a high-cadence
multi-color radial velocity campaign.  Measured at
sufficient precision, the mass could yield constraints on both the
planet's composition as well as its initial entropy
\citep{owen_constraining_2020}.

Separately, the Kepler data may still contain further information.
Although our transit timing study did not yield the detection of any
clearly significant planet-planet TTVs, the star's flaring may be
suggestive of star-planet interactions.  Appendix~\ref{app:flare}
highlights an odd flare timing coincidence that may be worthy of
further examination.

In the context of the known transiting planets, \pn\ is among the
youngest known (Figure~\ref{fig:rp_period_age}).  Comparable systems
with precise ages below 100\,Myr include K2-33b, DS~Tuc~Ab,
HIP~67522b, TOI~837b, AU~Mic~b, and the four-planet V1298~Tau system
\citep{Mann_K2_33b_2016,David_et_al_2017,newton_tess_2019,david_four_2019,bouma_cluster_2020,plavchan_planet_2020}.
\pn\ is currently the smallest of these systems ($\approx
3.3\,R_\oplus$), which may hint at selection effects in the young
planet sample \citep{zhou_2021_tois}.  Assuming that these planets
have masses between $\approx$5$\,M_\oplus$ and 20$\,M_\oplus$, their
large sizes and presumed low densities would be in accord with the
expectation that mini-Neptunes start their lives with large primordial
atmospheres that are shed over the first gigayear
\citep{Owen_Wu_2013,Fulton_et_al_2017,ginzburg_corepowered_2018}.  Our
suggestion of an aligned orbit differs from observed misalignments in
number of other close-in
mini-Neptunes~\citep{sanchis-ojeda_starspots_2011,albrecht_obliquities_2012,dalal_2019_hd3167,rubenzahl_tess-keck_2021}.
Unlike these older planets, \pn\ seems to have properties
consistent with a quiescent disk-driven migration history.  The
alternative scenario of in-situ formation is disfavored on theoretical
grounds: the required disk mass would likely drive migration, and so
lacks internal consistency
\citep{inamdar_formation_2015,ogihara_reassessment_2015}.

Ultimately, the main advance of this work was a precise measurement of
the age of \pn.   This age measurement was enabled by identifying the
connection of the star to the \cn\ using the Gaia data.  Table~\ref{tab:v06}
should enable similar cross-matches to
already known planets, as well as forthcoming planets from the TESS
mission \citep{ricker_transiting_2015,guerrero_tess_2021}.  An
alternative path toward age-dating more planets could be to identify kinematic associations
around known exoplanet host stars using positions and tangential velocities
from Gaia, and to then verify these associations with ancilliary
rotation periods and spectroscopy \citep[{\it e.g.},][]{tofflemire_tess_2021}.

@@

L.G.B{.} and J.L.C{.} are grateful to T{.}~David for help with the
transit fitting, to R{.}~Kerr for kindly providing us with the
\citet{Kerr2021} membership list prior to its publication.
L.G.B{.}, L.H{.}, and N.N{.} are also grateful to K{.}~Collins for
helping resolve the scheduling conflict that would have otherwise
prevented the MuSCAT3 observations.
% is grateful to G.~Zhou, B{.}~Tofflemire, A{.}~McWilliam,
% E{.}~Newton, M{.}~Kounkel, A{.}~Kraus, L{.}~Hillenbrand, and
% K{.}~Hawkins for the discussions on young stars, rotation, and lithium
% that encouraged this analysis.
%
L.G.B{.} acknowledges support by the TESS GI Program, programs
G011103 and G022117, through NASA grants 80NSSC19K0386 and
80NSSC19K1728.
%
L.G.B{.} was also supported by a Charlotte Elizabeth Procter
Fellowship from Princeton University.
%
The archival Keck/NIRC2 imaging was acquired by programs 2015A/N301N2L
(PI: A.~Kraus) and 2019A/N069 (PI: E.~Petigura).
%
In addition, this paper is based in part on observations made with the
MuSCAT3 instrument, developed by the Astrobiology Center and under
financial supports by JSPS KAKENHI (JP18H05439) and JST PRESTO
(JPMJPR1775), at Faulkes Telescope North on Maui, HI, operated by the
Las Cumbres Observatory.
%
This work is partly supported by JSPS KAKENHI Grant Numbers 22000005,
JP15H02063, JP17H04574, JP18H05439, JP18H05442, JST PRESTO Grant
Number JPMJPR1775, the Astrobiology Center of National Institutes of
Natural Sciences (NINS) (Grant Number AB031010).
%
% ACKNOWLEDGE PFS / CAMPANAS.
%
This paper also includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
We thank the TESS Architects (G.~Ricker, R.~Vanderspek, D.~Latham,
S.~Seager, J.~Jenkins) and the many TESS team members for their
efforts to make the mission a continued success.
%
%
%This study was based in part on observations at Cerro Tololo
%Inter-American Observatory at NSF's NOIRLab (NOIRLab Prop{.} ID
%2020A-0146; 2020B-0029 PI: Bouma), which is managed by the
%Association of Universities for Research in Astronomy (AURA) under a
%cooperative agreement with the National Science Foundation.
%
%
Finally, this research has made use of the Keck Observatory Archive (KOA),
which is operated by the W. M. Keck Observatory and the NASA Exoplanet
Science Institute (NExScI), under contract with the National
Aeronautics and Space Administration.  We also thank the Keck
Observatory staff for their support of HIRES and remote observing.  We
recognize the importance that the summit of Maunakea has within the
indigenous Hawaiian community, and are deeply grateful to have the
opportunity to conduct observations from this mountain.
%
% The Digitized Sky Survey was produced at the Space Telescope Science
% Institute under U.S. Government grant NAG W-2166.
% Figure~\ref{fig:scene} is based on photographic data obtained using
% the Oschin Schmidt Telescope on Palomar Mountain.
%

@@

\facilities{
 	{\it Astrometry}:
 	Gaia \citep{gaia_collaboration_gaia_2018,gaia_collaboration_2020_edr3}.
 	{\it Imaging}:
    Second Generation Digitized Sky Survey. %,
    %SOAR~(HRCam; \citealt{tokovinin_ten_2018}).
 	Keck:II~(NIRC2; \url{www2.keck.hawaii.edu/inst/nirc2}).
 	%Gemini:South~(Zorro; \citealt{scott_nessi_2018}.
 	Gemini:North~(`Alopeke; \citealt{scott_nessi_2018}.
 	{\it Spectroscopy}:
	%CTIO1.5$\,$m~(CHIRON; \citealt{tokovinin_chironfiber_2013}),
  %PFS ({\bf CITE}),
  %  MPG2.2$\,$m~(FEROS; \citealt{kaufer_commissioning_1999}),
	%AAT~(Veloce; \citealt{gilbert_veloce_2018}).
	%AAT~(HERMES; \citealt{lewis_2002_hermers_2df,sheinis_2015_hermes}),
 	Keck:I~(HIRES; \citealt{vogt_hires_1994}).
 	%VLT:Kueyen~(FLAMES; \citealt{pasquini_2002}).
% 	Euler1.2m~(CORALIE),
% 	ESO:3.6m~(HARPS; \citealt{mayor_setting_2003}).
 	{\it Photometry}:
%	  ASTEP:0.40$\,$m (ASTEP400),
% 	CTIO:1.0m (Y4KCam),
% 	Danish 1.54m Telescope,
%	  El Sauce:0.356$\,$m,
% 	Elizabeth 1.0m at SAAO,
% 	Euler1.2m (EulerCam),
	  Kepler \citep{borucki_kepler_2010},
% 	Magellan:Baade (MagIC),
% 	Max Planck:2.2m	(GROND; \citealt{greiner_grond7-channel_2008})
    MuSCAT3 \citep{Narita_2020},
% 	NTT,
% 	SOAR (SOI),
 	  TESS \citep{ricker_transiting_2015}.
% 	TRAPPIST \citep{jehin_trappist_2011},
% 	VLT:Antu (FORS2).
}

@@

		\vspace{-0.1cm}
		\subfloat{
			\includegraphics[width=0.55\textwidth]{f6.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Kepler 1627 is a binary.} {\it Top:} High-resolution imaging
    from Gemini-North/`Alopeke ({\it left}) and Keck/NIRC2 ({\it
    right}) shows an $\approx$M2V companion at $\rho \approx
    0\farcs16$, which corresponds to a projected separation of
    $53\pm7$\,AU.  {\it Bottom:} Gaia EDR3 renormalized unit weight
    error (RUWE) point estimates for Kepler\,1627A and other members
    of the $\delta$\,Lyr cluster reported by \citet{KounkelCovey2019}.  Since other members of the cluster
    with similar colors have comparable degrees of photometric
    variability, the high RUWE suggests that Kepler\,1627 is an
    astrometric binary. 
    \label{fig:kep1627binary}
	}
\end{figure*}

We first noted the presence of a stellar neighbor in archival
Keck/NIRC2 Kp-band adaptive optics imaging (2.12\,$\mu $m), from the
Spring semesters of both 2015 and 2019.  We acquired additional
Gemini-North/`Alopeke speckle imaging on 24 June 2021, which showed
the same companion in the 0.83\,$\mu$m notch filter, but not the
$0.56\,\mu$m filter.  Figure~\ref{fig:kep1627binary} summarizes the
results of the high-resolution imaging.  Although the companion is
unresolved in the Gaia source catalog, its existence was also
suggested by the primary star's large RUWE, relative to other members
of the \cn.  The images yield a projected separation $\rho \approx
0\farcs16$, with $\Delta m_{832} \approx 3.1$ and $\Delta m_{\rm Kp} =
2.5$.  Using the measured Gaia EDR3 parallax for the system, this
implies a projected separation of $53 \pm 7$.  Given the low geometric
probably of a star imaged within $\rho \approx 0\farcs16$ to be a
chance companion along the line of sight, and the large observed RUWE,
we proceed under the assumption that the companion is bound, and that
the Kepler\,1627 system is binary.  Based on the
tabulation\footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt},
version \texttt{2021/03/02}.} by \citet{pecaut_mamajek_2013}, the
measured magnitude differences for a G8V primary correspond to a
spectral type for the companion of $\approx$M2V ($M_\star \approx
0.44\,M_\odot$).  However, the companion should have a longer
pre-main-sequence contraction phase than the primary, which would
imply that this mass is overestimated by $\sim10$ to $20\%$.

>>>>

Comparing our young star list against the Kepler field yielded two
discoveries.  The first, to be discussed in an upcoming analysis by
J.~Curtis et al{.}, is that Kepler observed the $\approx$350\,Myr open
cluster Theia~520 (UBC~1).  At least six Kepler planets are known in
the cluster from the Kepler-52 and Kepler-968 systems
\citep{rowe_validation_2014,jontof-hutter_following_2021}.  The second
discovery, and the focus of this work, is that Kepler observed a
portion of the $\delta$\,Lyr cluster (Stephenson-1; Theia~73;
\citealt{stephenson_possible_1959}).  Figure~\ref{fig:skychart} shows
the overlap between the Kepler field and the cluster.

A previous clustering analysis of the Gaia data reported that
Kepler\,1627 (KIC 6184894; KOI 5245; TIC 120105470) is a member of the
\cn\ \citep{kounkel_untangling_2019}.  Given the previous statistical
validation the close-in mini-Neptune Kepler 1627b
\citep{2012ApJS..199...24T,morton_false_2016,thompson_planetary_2018},
we examined the age of the star and its putative host cluster more
closely (Section~\ref{sec:cluster}).  We find that the $\delta$ Lyr
cluster is \clusterage\ old, and that \sn\ is indeed a member of the
cluster.  Focusing on the planet itself, we confirm that despite the
presence of a previously unreported binary companion, the planet
orbits the G-dwarf primary on an orbit that is likely aligned with the
stellar rotation axis (Section~\ref{sec:planet}).  We conclude by
highlighting broader implications for our ability to age-date a
statistical sample of planets (Section~\ref{sec:conc}).

@@

The final piece of evidence comes from a spectroscopic transit we
observed using Keck/HIRES during the night of 7 Aug 2021 (UT).  We
used the iodine cell for the wavelength calibration, and scheduled the
transit using the ephemeris of \citet{holczer_transit_2016}.  We also acquired
simultaneous multi-band photometry using MuSCAT3 \citep{Narita_2020}.
The lower panels in Figure~\ref{fig:obliquity} show the results.  The
photometry shows the expected starspot trend, along with the transit
and a likely starspot crossing event at ${\rm JD} - 2459433 = 0.955$.
The radial velocities show significant scatter, and an
increase in RV is seen shortly after the expected ingress time.  The
internal uncertainty on the RVs ($\approx 15\,{\rm m\,s}^{-1}$) is
dominated by the $v\sin i$ broadening.

@@

We fitted the RVs using the \citet{hirano_analytic_2010,hirano_2011}
models for the Rossiter-McLaughlin (RM) effect, and allowed the
sky-projected obliquity, the stellar equatorial velocity, and the
Gaussian dispersion of the spectral lines to vary.  We also allowed
for an optional linear and quadratic trend, and a white-noise jitter
term.  The quadratic model with the RM effect is shown in
Figure~\ref{fig:obliquity}; the prior on $v\sin i$ has been assumed
from Table~\ref{tab:starparams}, and the jitter term is included.
We found $\chi^2_{\rm red} =
5.4$ for the best-fitting linear case, and $\chi^2_{\rm red} = 4.4$
for the best-fitting quadratic, with a $\Delta {\rm BIC} = {\rm
BIC}_{\rm line} - {\rm BIC}_{\rm quad} = 19.6$ and $\Delta {\rm AIC} =
{\rm AIC}_{\rm line} - {\rm AIC}_{\rm quad} = 20.6$.  While this
provides strong statistical evidence to prefer the quadratic model
over the linear one, the $\chi^2_{\rm red}$ indicate that neither fit
is very good.  Considering a quadratic trend without any RM
effect yields $\chi^2_{\rm red} = 4.3$, and $\Delta {\rm BIC} = {\rm
BIC}_{\rm trend} - {\rm BIC}_{\rm quad} = 1.9$ ($\Delta {\rm
AIC}=5.2$).  From a model-comparison standpoint, there is therefore
only marginal statistical evidence to prefer the best-fitting ``RM and
quadratic trend'' model over the best-fitting ``quadratic trend only''
model.  Given the expected semi-amplitude of the velocity anomaly
($\Delta v_{\rm RM}\approx 20\,{\rm m\,s}^{-1}$) and the achieved precision,
we cannot claim a detection of the Doppler transit.
From the MuSCAT3 data however, we do know that the transit
was observed, and the increase in radial velocity seen shortly after
ingress is more consistent with a prograde or polar orbit than a
retrograde orbit.  Fixing the orbit to be either exactly prograde or
exactly retrograde, we find $\Delta {\rm BIC} = {\rm BIC}_{\rm
retrograde} - {\rm BIC}_{\rm trend} = 18.0$; the retrograde case is
ruled out on this basis.  More data will be needed however to
make a more precise measurement of the stellar obliquity.

@@

Kepler\,1627Ab provides a new extremum in the ages of the Kepler
planets, and opens multiple avenues for further study.  Further
observations of Doppler transits could yield a more precise stellar
obliquity, and could confirm or refute the expected prograde orbital
geometry.  Similarly, transit spectroscopy aimed at detecting outflows
of hydrogen or helium could yield insight into the evolutionary state
of the atmosphere \citep[{\it
e.g.},][]{spake_helium_2018,vissapragada_2020}.  Determining the
precise level of high-energy irradiation incident on the planet would
also help in clarifying the expected outflow rate \citep[{\it
e.g.},][]{poppenhaeger_2021}.  Finally, perhaps the most challenging,
but also the most informative measurement would be to determine the
planet's mass.  This might be possible either through detailed timing
analyses of the Kepler data, or through a high-cadence multi-color
radial velocity campaign.  Measured at sufficient precision, the mass
could yield constraints on both the planet's composition and its
initial entropy \citep{owen_constraining_2020}.

Separately, the Kepler data may yet contain further information.
Although our transit timing study did not yield the detection of any
clearly significant planet-planet TTVs, the star's flaring may be
suggestive of star-planet interactions.  Appendix~\ref{app:flare}
highlights an odd flare timing coincidence that may be worthy of
further examination.

In the context of the known transiting planets, \pn\ is among the
youngest known (Figure~\ref{fig:rp_period_age}).  Comparable systems
with precise ages below 100\,Myr include K2-33b, DS~Tuc~Ab,
HIP~67522b, TOI~837b, AU~Mic~b, and the four-planet V1298~Tau system
\citep{Mann_K2_33b_2016,David_et_al_2017,newton_tess_2019,david_four_2019,bouma_cluster_2020,plavchan_planet_2020}.
\pn\ is currently the smallest of these systems ($\approx
3.3\,R_\oplus$), which may hint at selection effects in the young
planet sample \citep{zhou_2021_tois}.  Assuming that these planets
have masses between $\approx$5$\,M_\oplus$ and 10$\,M_\oplus$, their
large sizes and presumed low densities would be in accord with the
expectation that mini-Neptunes start their lives with large primordial
atmospheres that are shed over the first gigayear
\citep{Owen_Wu_2013,Fulton_et_al_2017,ginzburg_corepowered_2018}.  Our
suggestion of an aligned orbit differs from observed misalignments in
number of close-in
mini-Neptunes~\citep{sanchis-ojeda_starspots_2011,albrecht_obliquities_2012,dalal_2019_hd3167,rubenzahl_tess-keck_2021}.
Unlike these older planets, \pn\ seems to have properties consistent
with a quiescent disk-driven migration history.  The alternative
scenario of in-situ formation is disfavored on theoretical grounds:
the required disk mass would likely drive migration, and so lacks
internal consistency
\citep{inamdar_formation_2015,ogihara_reassessment_2015}.

Ultimately, the main advance of this work was a precise measurement of
the age of \pn.   The age measurement was enabled by identifying the
connection of the star to the \cn\ using the Gaia data.
Table~\ref{tab:v06} should enable similar cross-matches to already
known planets, as well as forthcoming planets from the TESS mission
\citep{ricker_transiting_2015,guerrero_tess_2021}.  An alternative
path toward age-dating more planets could be to identify kinematic
associations around known exoplanet host stars using positions and
tangential velocities from Gaia, and to then verify these associations
with ancilliary rotation periods and spectroscopy \citep[{\it
e.g.},][]{tofflemire_tess_2021}.

@@

The authors are grateful to T{.}~David for help with the transit
fitting, to R{.}~Kerr for kindly providing us with the
\citet{Kerr2021} membership list prior to its publication, and to
J{.}~Winn for helpful discussions on the RM observations and flare
timing.
L.G.B{.}, L.H{.}, and N.N{.} are also grateful to K{.}~Collins for
helping resolve the scheduling conflict that would have otherwise
prevented the MuSCAT3 observations.
% is grateful to G.~Zhou, B{.}~Tofflemire, A{.}~McWilliam,
% E{.}~Newton, M{.}~Kounkel, A{.}~Kraus, L{.}~Hillenbrand, and
% K{.}~Hawkins for the discussions on young stars, rotation, and lithium
% that encouraged this analysis.
%
L.G.B{.} acknowledges support by the TESS GI Program, programs
G011103 and G022117, through NASA grants 80NSSC19K0386 and
80NSSC19K1728.
%
L.G.B{.} was also supported by a Charlotte Elizabeth Procter
Fellowship from Princeton University.
%
The archival Keck/NIRC2 imaging was acquired by programs 2015A/N301N2L
(PI: A.~Kraus) and 2019A/N069 (PI: E.~Petigura).
%
In addition, this paper is based in part on observations made with the
MuSCAT3 instrument, developed by the Astrobiology Center and under
financial supports by JSPS KAKENHI (JP18H05439) and JST PRESTO
(JPMJPR1775), at Faulkes Telescope North on Maui, HI, operated by the
Las Cumbres Observatory.
%
This work is partly supported by JSPS KAKENHI Grant Numbers 22000005,
JP15H02063, JP17H04574, JP18H05439, JP18H05442, JST PRESTO Grant
Number JPMJPR1775, the Astrobiology Center of National Institutes of
Natural Sciences (NINS) (Grant Number AB031010).
%
% ACKNOWLEDGE PFS / CAMPANAS.
%
This paper also includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
We thank the TESS Architects (G.~Ricker, R.~Vanderspek, D.~Latham,
S.~Seager, J.~Jenkins) and the many TESS team members for their
efforts to make the mission a continued success.
%
%
%This study was based in part on observations at Cerro Tololo
%Inter-American Observatory at NSF's NOIRLab (NOIRLab Prop{.} ID
%2020A-0146; 2020B-0029 PI: Bouma), which is managed by the
%Association of Universities for Research in Astronomy (AURA) under a
%cooperative agreement with the National Science Foundation.
%
%
Finally, this research has made use of the Keck Observatory Archive (KOA),
which is operated by the W. M. Keck Observatory and the NASA Exoplanet
Science Institute (NExScI), under contract with the National
Aeronautics and Space Administration.  We also thank the Keck
Observatory staff for their support of HIRES and remote observing.  We
recognize the importance that the summit of Maunakea has within the
indigenous Hawaiian community, and are deeply grateful to have the
opportunity to conduct observations from this mountain.
%
% The Digitized Sky Survey was produced at the Space Telescope Science
% Institute under U.S. Government grant NAG W-2166.
% Figure~\ref{fig:scene} is based on photographic data obtained using
% the Oschin Schmidt Telescope on Palomar Mountain.
%

@@

\facilities{
 	{\it Astrometry}:
 	Gaia \citep{gaia_collaboration_gaia_2018,gaia_collaboration_2020_edr3}.
 	{\it Imaging}:
    Second Generation Digitized Sky Survey. %,
    %SOAR~(HRCam; \citealt{tokovinin_ten_2018}).
 	Keck:II~(NIRC2; \url{www2.keck.hawaii.edu/inst/nirc2}).
 	%Gemini:South~(Zorro; \citealt{scott_nessi_2018}.
 	Gemini:North~(`Alopeke; \citealt{scott_nessi_2018,scott_twin_2021}.
 	{\it Spectroscopy}:
	%CTIO1.5$\,$m~(CHIRON; \citealt{tokovinin_chironfiber_2013}),
  %PFS ({\bf CITE}),
  %  MPG2.2$\,$m~(FEROS; \citealt{kaufer_commissioning_1999}),
	%AAT~(Veloce; \citealt{gilbert_veloce_2018}).
	%AAT~(HERMES; \citealt{lewis_2002_hermers_2df,sheinis_2015_hermes}),
 	Keck:I~(HIRES; \citealt{vogt_hires_1994}).
 	%VLT:Kueyen~(FLAMES; \citealt{pasquini_2002}).
% 	Euler1.2m~(CORALIE),
% 	ESO:3.6m~(HARPS; \citealt{mayor_setting_2003}).
 	{\it Photometry}:
%	  ASTEP:0.40$\,$m (ASTEP400),
% 	CTIO:1.0m (Y4KCam),
% 	Danish 1.54m Telescope,
%	  El Sauce:0.356$\,$m,
% 	Elizabeth 1.0m at SAAO,
% 	Euler1.2m (EulerCam),
	  Kepler \citep{borucki_kepler_2010},
% 	Magellan:Baade (MagIC),
% 	Max Planck:2.2m	(GROND; \citealt{greiner_grond7-channel_2008})
    MuSCAT3 \citep{Narita_2020},
% 	NTT,
% 	SOAR (SOI),
 	  TESS \citep{ricker_transiting_2015}.
% 	TRAPPIST \citep{jehin_trappist_2011},
% 	VLT:Antu (FORS2).
}

@@

		\vspace{-0.1cm}
		\subfloat{
			\includegraphics[width=0.55\textwidth]{f6.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Kepler 1627 is a binary.} {\it Top:} High-resolution imaging
    from Gemini-North/`Alopeke ({\it left}) and Keck/NIRC2 ({\it
    right}) shows an $\approx$M2V companion at $\rho \approx
    0\farcs16$, which corresponds to a projected separation of
    $53\pm4$\,AU.  {\it Bottom:} Gaia EDR3 renormalized unit weight
    error (RUWE) point estimates for Kepler\,1627A and other members
    of the $\delta$\,Lyr cluster reported by \citet{KounkelCovey2019}.
    Since other members of the cluster with similar colors have
    comparable degrees of photometric variability, the high RUWE
    suggests that Kepler\,1627 is an astrometric binary. 
    \label{fig:kep1627binary}
	}
\end{figure*}

We first noted the presence of a stellar neighbor in archival
Keck/NIRC2 Kp-band adaptive optics imaging (2.12\,$\mu $m), from the
Spring semesters of both 2015 and 2019.  We acquired additional
Gemini-North/`Alopeke speckle imaging on 24 June 2021, which showed
the same companion in the 0.83\,$\mu$m notch filter, but not the
$0.56\,\mu$m filter.  Figure~\ref{fig:kep1627binary} summarizes the
results of the high-resolution imaging.  Although the companion is
unresolved in the Gaia source catalog, its existence was also
suggested by the primary star's large RUWE, relative to other members
of the \cn.  The images yield a projected separation $\rho \approx
0\farcs16$, with $\Delta m_{832} \approx 3.1$ and $\Delta m_{\rm Kp} =
2.5$.  Using the measured Gaia EDR3 parallax for the system, this
implies a projected separation of $53 \pm 4$.  Given the large
observed RUWE of the primary, and the low geometric probability that a
companion imaged within $\rho \approx 0\farcs16$ is a chance
line-of-sight companion, we proceed under the assumption that the
companion is bound, and that Kepler\,1627 system is a binary.  Based
on the
tabulation\footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt},
version \texttt{2021/03/02}.} by \citet{pecaut_mamajek_2013}, the
measured magnitude differences for a G8V primary correspond to a
spectral type for the companion of $\approx$M2V ($M_\star \approx
0.44\,M_\odot$).  However, the companion should have a longer
pre-main-sequence contraction phase than the primary, which would
imply that this mass is overestimated by $\sim10$ to $20\%$.
